Check interior point method

### 2017-01-02 analysis/checkIP.Rmd
Successfully rendered checkIP.Rmd using new dsc-opt and dsc-shrink output.

@@

# Select out the lfsr estimates for each method.
df1 = res$lfsr %>% filter(method %in% c("ash.hu.nocxx")) %>% 
        select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
        melt(id.vars = c("method","scenario","seed",".id"),
             value.name = "lfsr.nocxx")
df2 = res$lfsr %>% filter(method %in% c("ash.hu")) %>%
        select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
        melt(id.vars = c("method","scenario","seed",".id"),
             value.name = "lfsr.IP")
df = inner_join(df1,df2,by = c("scenario","seed","variable"))
ggplot(df,aes(lfsr.nocxx,lfsr.IP)) + geom_point(shape = 1) +
facet_wrap(~ scenario,nrow = 2) +
geom_abline(colour = "black") +
xlab("EM algorithm (no cxx)") +
ylab("IP method")
```

>>>>

**Note:** the last code chunk ("compare_lfsr") may take several minutes to 
render in R or RStudio because it uses ggplot to plot more than a million data 
points. Also, it it may not be possible to run the last code chunk 
interactively in RStudio.

@@

# Select out the lfsr estimates for each method.
df1 = res$lfsr %>% filter(method %in% c("ash.hu.nocxx")) %>% 
        select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
        melt(id.vars = c("method","scenario","seed",".id"),
             value.name = "lfsr.nocxx")
df2 = res$lfsr %>% filter(method %in% c("ash.hu")) %>%
        select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
        melt(id.vars = c("method","scenario","seed",".id"),
             value.name = "lfsr.IP")
df = inner_join(df1,df2,by = c("scenario","seed","variable"))
df = transform(df,scenario = factor(scenario))
print(ggplot(df,aes(lfsr.nocxx,lfsr.IP)) + 
      geom_point(shape = 1) +
      facet_wrap(~ scenario,nrow = 2) +
      geom_abline(colour = "black") +
      xlab("EM algorithm (no cxx)") +
      ylab("IP method"))
```
